Automated segmentation of WMHs

### 2017-08-08 Presentation/wmh.Rmd
ENH:  notes.

@@

@@

@@

@@

@@

@@

<!--
Evaluation measures for both Stages of the leave-one-out protocol of the described protocol 
in the Methods section:  (a) sensitivity, (b) positive predictive value, (c) $F_1$ score, 
and (d) relative volume difference.   These quantitative assessments are given for three 
quantile ranges spanning the range of the manually-derived lesion volumes.    Overall 
improvement in all three whole lesion-based measuers is seen as the second Stage RF model is 
applied for all three quantile ranges.  The relative volume difference corresponding to the 
Stage 2 results tend to predict a decreased predicted volume over the Stage 1 results.
-->

@@

* Takes a lot of time for new data
    1. Create initial set of feature images
    2. Run it through Stage 1 model
    3. Create more feature images
    4. Run subject through Stage 2 model
* Relatively small data set
* Evaluation/modeling limited to a single site
* Creativity
    * Feature image selection
    * Are we choosing discriminative features?
* Imbalanced data
* No comparison with clinical data

@@

* Potentially quicker for new data
    * Build initial model takes time 
    * No feature images to create for new data
    * GPU
* Optimization learns the features
* Mature packages
    * TensorFlow, CNTK, Torch, Theano, Sci-TK, Caffe, mxnet, Keras
* Need lots of training data

@@

## Imbalanced data

>>>>

<!--

* This is an update respecting current work.
* We published this work in March 2016.
* Have since gained access to the larger multi-site CENC data set.

-->

@@

<!--

* This is the current pipeline.
* From training data (produced by James Stone), 
    * we generate feature images from the multi-modal training data (T1, T2, FLAIR),
    * we then build a 2-layer random forest model
    * A mean shape/intensity symmetric template is used for input
* To segment an individual subject
    * multi-modal image input
    * generate feature images
    * pass through RF model

-->

@@

<!--

* For many machine learning algorithms, as in the case of 
  random forests, one of the most creative design aspects is
  determining which feature images one should use.
* This table is the list of feature images.
* It should be noted that these take an hour plus to generate.
  This time is for both training the random forest models
  and pushing each new subject through the finished pipeline.
* We will contrast these two characteristics 1) feature images 
  and 2) time as differences with future work.

-->

@@

<!--

* The functional dependence is illustrated by this equation:
    the label at each voxel (i.e., what tissue type) is dependent on the
    the weighted combination of all the features at that voxel.
* Below are axial examples of the set of feature images used to discriminate
  between the different tissue types.

-->

@@

<!--

* The pipeline, as shown on slide 3, utilizes two concatenated random forest models
  where the output of the first is used as partial input to the second.
* When generating the RF models during training, we can get a sense of the
  "importance" of each of the features.

-->

@@

<!--

* Here are sample results:
   * From Site 1 only 
   * Used a leave-one-out evaluation strategy.
       - take the ~25 subjects generated by James Stone
       - use 24 to create the RF models and then test on the remaining subject

-->

@@

<!--

* These are the evaluation measures showing improvement for the two "stages".
    * We used 
        - (a) sensitivity 
        - (b) positive predictive value
        - (c) F_1 score
        - (d) relative volume difference.
* Overall improvement in all three whole lesion-based measuers is seen as the second 
  Stage RF model is applied for all three quantile ranges. 
* The relative volume difference corresponding to the Stage 2 results tend to predict 
  a decreased predicted volume over the Stage 1 results.

-->

@@

* Takes a lot of time for new data
    1. Create initial set of feature images
    2. Run it through Stage 1 model
    3. Create more feature images
    4. Run subject through Stage 2 model
* We are using a relatively small training data set
* Modeling/training is limited to a single site
* Creative engineering is needed
    * Feature image selection
    * Are we choosing discriminative features?
* We have imbalanced data (e.g., way more GM than WMH voxels)
* No comparisons with clinical data (yet)

@@

* Exciting new possibilities with deep learning
* Potentially quicker for new data
    * Building initial model takes time __but__
    * no feature images are needed to create for new data.
* Optimization and architecture are used to learn the features
* Mature packages
    * TensorFlow, CNTK, Torch, Theano, Sci-TK, Caffe, mxnet, Keras
* Need lots of training data

@@

## Quick note on imbalanced data
